Weather Data Integration and Assimilation System\\

### 2020-02-10 results/sec_2-workload.tex
Add test cases as list

The test plans mentioned in \ref{se:test_plan} are implemented via the \acrshort{jmeter}. The \ref{fi:wdias_performance_test} shows the overall figure of all the test cases.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{results/work_load/wdias_performance_test.png}
    \caption{WDIAS Performance Test Cases}
    \label{fi:wdias_performance_test}
\end{figure}

\dbc{Try to list names of test cases than having these black screenshots. Same for other places.}

>>>>

The test plans mentioned in \ref{se:test_plan} are implemented via the \acrshort{jmeter}. The following list shows the all the test cases using for the performance testing.

\begin{itemize}
    \item User Defined Variables
    \item Setup thread group
    \item Create Timeseries thread group
    \item Create Extensions thread group
    \item Load Test Timeseries Concurrency thread group
    \item Load Test Timeseries Concurrency thread group
    \item Test Flow thread group
\end{itemize}
